\mireval{}

### 2014-05-08 paper/paper.tex
Revision revisions

\begin{document}
%
\maketitle
%
\begin{abstract}
Central to the field of MIR research is the evaluation of algorithms used to extract information from music data.
We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
In the present work, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to an existing implementation.
When the score reported by \mireval{} differs substantially from the reference, we detail the differences in implementation.
We also provide a brief overview of \mireval{}'s architecture, design, and intended use.
\end{abstract}
%
\section{Evaluating MIR Algorithms}

@@

% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
For the past 10 years, the yearly Music Information Retrieval Evaluation eXchange (MIREX) has been a forum for comparing MIR algorithms over common datasets \cite{downie2008music}.
By providing a standardized shared-task setting, MIREX has become critically useful to track progress in MIR research.
MIREX is built upon the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
The NEMA codebase includes multiple programming languages and dependencies (some of which, e.g. Matlab, are proprietary) so compiling and running it at individual sites is nontrivial. 
%
%Due to its scale, characteristics, and intended use, 
In consequence, the NEMA system is rarely used for evaluating MIR algorithms outside of the setting of MIREX \cite{downie2008music}.
Instead, researchers typically create their own implementations of common metrics for evaluating their algorithms.
These implementations are thus not standardized, and may contain differences in details, or even bugs, that confound comparisons.

These factors motivate the development of a standardized software package which implements the most common metrics used to evaluate MIR systems.
Such a package should be straightforward to use and well-documented so that it 
presents a preferable alternative to in-house development for MIR researchers.
In addition, it should be community-developed and transparently implemented so that all design decisions are easily understood and open to discussion and improvement.

@@

\begin{table*}[t]
  \centering
\begin{tabular}{c c c c c c c c c c}
\toprule
 \multicolumn{5}{ c }{Chord} & \multicolumn{5}{ c }{Melody}\\
  \cmidrule(lr){1-5}

  \cmidrule(lr){5-10}
 Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
  0.007 & 0.1634 & 1.005 & 0.483 & 0.899 & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
  \midrule
 \multicolumn{10}{ c }{Segmentation} \\
  \cmidrule(lr){1-10}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5       & F@3 \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\% &    0.393\% \\
  \midrule
 \multicolumn{4}{ c }{Segmentation} & \multicolumn{6}{ c }{Beat}\\
  \cmidrule(lr){1-4}
  \cmidrule(lr){5-10}
  P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt \\
  0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% \\
  \midrule
 \multicolumn{3}{ c }{Beat} & \multicolumn{7}{ c }{Pattern}\\
  \cmidrule(lr){1-3}
  \cmidrule(lr){4-10}
  AMLc       & AMLt       & In. Gain & Pat & Pat & Pat & Pat & Pat & Pat & Pat \\
  0.137\% &    0.139\% &   9.174\% &  ??? & ??? & ??? & ??? & ??? & ??? & ???\\
  \midrule
 \multicolumn{10}{ c }{Pattern}\\
  \cmidrule(lr){1-10}
  Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat\\
  ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ???\\
  \midrule
 \multicolumn{4}{ c }{Pattern}  & \multicolumn{3}{ c }{Onset}  & \multicolumn{3}{ c }{Source Separation}\\
  \cmidrule(lr){1-4}
  \cmidrule(lr){5-7}
  \cmidrule(lr){8-10}
 Pat & Pat & Pat & Pat & F-measure  & Precision  & Recall & SDR & SIR & SAR \\
 ??? & ??? & ??? & ??? &    0.165\% &    0.165\% &    0.165\% & ??? & ??? & ??? \\
  \bottomrule

>>>>

\begin{document}
%
\maketitle
%
\begin{abstract}
Central to the field of MIR research is the evaluation of algorithms used to extract information from music data.
We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
In this paper, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to  existing implementations.
When the scores reported by \mireval{} differ substantially from the reference, we detail the differences in implementation.
We also provide a brief overview of \mireval{}'s architecture, design, and intended use.
\end{abstract}
%
\section{Evaluating MIR Algorithms}

@@

% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
For the past 10 years, the yearly Music Information Retrieval Evaluation eXchange (MIREX) has been a forum for comparing MIR algorithms over common datasets \cite{downie2008music}.
By providing a standardized shared-task setting, MIREX has become critically useful to track progress in MIR research.
MIREX is built upon the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
The NEMA codebase includes multiple programming languages and dependencies (some of which, e.g. Matlab, are proprietary) so compiling and running it at individual sites is nontrivial. 
%
%Due to its scale, characteristics, and intended use, 
In consequence, the NEMA system is rarely used for evaluating MIR algorithms outside of the setting of MIREX \cite{downie2008music}.
Instead, researchers often create their own implementations of common metrics for evaluating their algorithms.
These implementations are thus not standardized, and may contain differences in details, or even bugs, that confound comparisons.

These factors motivate the development of a standardized software package which implements the most common metrics used to evaluate MIR systems.
Such a package should be straightforward to use and well-documented so that it can be easily adopted by MIR researchers.
In addition, it should be community-developed and transparently implemented so that all design decisions are easily understood and open to discussion and improvement.

@@

\begin{table*}[t]
  \centering
\begin{tabular}{c c c c c c c c c c}
\toprule
 \multicolumn{5}{ c }{Chord} & \multicolumn{5}{ c }{Melody}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){5-10}
 Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
 ??? & ??? & ??? & ??? & ??? & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
  \midrule
 \multicolumn{10}{ c }{Segmentation} \\
  \cmidrule(lr){1-10}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5       & F@3 \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\% &    0.393\% \\
  \midrule
 \multicolumn{4}{ c }{Segmentation} & \multicolumn{6}{ c }{Beat}\\
  \cmidrule(lr){1-4}
  \cmidrule(lr){5-10}
  P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt \\
  0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% \\
  \midrule
 \multicolumn{3}{ c }{Beat} & \multicolumn{7}{ c }{Pattern}\\
  \cmidrule(lr){1-3}
  \cmidrule(lr){4-10}
  AMLc       & AMLt       & In. Gain & Pat & Pat & Pat & Pat & Pat & Pat & Pat \\
  0.137\% &    0.139\% &   9.174\% &  ??? & ??? & ??? & ??? & ??? & ??? & ???\\
  \midrule
 \multicolumn{10}{ c }{Pattern}\\
  \cmidrule(lr){1-10}
  Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat\\
  ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ???\\
  \midrule
 \multicolumn{4}{ c }{Pattern}  & \multicolumn{3}{ c }{Onset}  & \multicolumn{3}{ c }{Source Separation}\\
  \cmidrule(lr){1-4}
  \cmidrule(lr){5-7}
  \cmidrule(lr){8-10}
 Pat & Pat & Pat & Pat & F-measure  & Precision  & Recall & SDR & SIR & SAR \\
 ??? & ??? & ??? & ??? &    0.165\% &    0.165\% &    0.165\% & ??? & ??? & ??? \\
  \bottomrule
